### 2014-10-20 ThesisJo/derivations.tex
la2pdf commit - 2014:10:20	17:09:58	(Mon20.Oct)

\begin{figure}[th]
\graphicsAI[drawing]{gfx/roughness.svg}
\end{figure}

>>>>

For a plane monochromatic wave the Rayleigh roughness parameter is quantified by:
\begin{align}
\Delta\varphi = 2k\xi\cos\theta.
\end{align}
Here $\theta$ is the incidence angle, $k = \frac{2\pi}{\lambda}$ is the wavenumber of the incoming wave, $\xi$ is the distance from the scattering point to the mean surface plane, and $\Delta\varphi$ is the phase difference.

\begin{figure}[th]
\graphicsAI[drawing,width=\linewidth]{gfx/roughness.svg}
\end{figure}

To see how roughness affects the specular reflection we compute the mean reflected wave as
\begin{align}
<p> &= \int\limits_{-\infty}^{\infty} e^{-j\Delta\varphi(\xi)} p(\xi) d\xi,
\end{align}
where $p(\xi)$ is the probability density function of $\xi$. If we assume normal distribution, we get:
\begin{align}
<p> &= \int\limits_{-\infty}^{\infty} e^{-j2k\xi\cos\theta} \frac{1}{\sqrt{2\pi}\sigma_{\!\xi}}e^{-\frac{\xi^2}{2\sigma_{\!\xi}^2}} d\xi \nn
&= \frac{1}{\sqrt{2\pi}\sigma_{\!\xi}} \int\limits_{-\infty}^{\infty} e^{-j2k\xi\cos\theta} e^{-\frac{\xi^2}{2\sigma_{\!\xi}^2}} d\xi \nn
\end{align}
